---
title: "cp7_assignment_instructions"
author: "Aidan O'Hara"
date: "2023-08-21"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Function**als** 

### Exercise 1


```{r echo = FALSE}
matrix(c(7,32,49,0,2, 111:121, 2, 17, 70, 77), nrow = 5, ncol = 4)
```
Construct the above matrix and assign it to the variable `anotherMatrix`

Use the apply function to calculate the following.

`anotherMean`: the means of each row of `anotherMatrix`.

`yetAnotherMean`: the means of each column of `anotherMatrix`.

`sortedRows`: where the columns of `anotherMatrix` are sorted in ascending order.

### Exercise 2
Use `lapply`, `sapply` and `mapply` on the `mtcars` dataframe to get the minimum value of each column. 

`l <- lapply()`

`s <- sapply()`

`m <- mapply()`

Make a list of the three new objects, assigned to `listOfApplys`

Then use `sapply` to return the `class` of each element of the `listOfApplys`, assign it to `typesOfApplies`.

### Exercise 3

# Titanic

Use the apply family to create the following tables (read `matrix`) about the built-in `Titanic` dataset.

The sum of males vs females aboard. Assigned to `passengersBySex`.

The sum of survivors vs sex. Assigned to `survivorsBySex`.

The sum of males vs females aboard. Assigned to `passengersBySexByAge`.

### Exercise 4

Use the apply family and the built-in `iris` dataset to generate plots!  You'll need to run `install.packages("vioplot")` in the console, and include `library(vioplot)` in your submission too.

First, create a boxplot for each numeric column of the `iris` dataset. (four boxplots), assign your apply call to the variable `box`.

`box <- apply()`

Next, construct a violin plot for each numeric column, remove the numbers from the x-axis, and specify `color = "salmon"`, assign your apply call to the variable `violin`.

`violin <- apply()`